%!TEX TS-program = xelatex
\documentclass[]{friggeri-cv}
\begin{document}
\header{Miguel A.}{Garzón}
       {Software Engineer, EIT}

\section{Interests}
Reverse Engineering, model driven development, test driven development, software development methodologies.

\section{Summary of qualifications}

\begin{itemize}
\item Graduate Student in Bachelor in Applied Science, Software Engineering
\item Over 4 years of experience in Software Engineering (Programming, Software Development)
\item Excellent interpersonal and teamwork skills
\item Experience in conducting research in both academic and industrial sittings
\item Professional level of communication skills in English, French and Spanish
\end{itemize}

\section{Awards and Scholarships}
\begin{entrylist}
  \entry
    {2015}
    {Part-Time Professor of the year}
    {University of Ottawa}
    {Faculty of Engineering}
 \entry
    {2014-2015}
    {University of Ottawa Excellence Scholarship}
    {University of Ottawa}
    {}
 \entry
    {2011}
    {Transferred from the Master's to the Ph.D. program}
    {University of Ottawa}
    {}
     \entry
    {2010 to 2013}
    {Ontario Graduate Scholarship (x3)}
    {University of Ottawa}
    {}
    \entry
    {2008-2009}
    {Dean’s Honour List}
    {University of Ottawa}
    {}
    \entry
    {2005-2007}
    {Nortel’s Bursary}
    {University of Ottawa}
    {}
    \entry
    {2005}
    {Admission Scholarship}
    {University of Ottawa}
    {}
\end{entrylist}

\section{Professional Experience}
\textbf{Software Researcher} - 
University of Ottawa, ON
\begin{flushright}  
September 2010 - Present \\
\end{flushright}   
\begin{itemize}
\item Research in reverse engineering is focused on developing iterative, tool-supported frameworks for incremental and semi-automatic design recovery and analysis of software systems written in Java and C++. 
\end{itemize}

\textbf{Part-time Professor and Teaching Assistant of Computer and Software Engineering} \\ 
University of Ottawa, ON
\begin{flushright}   
September 2010 - Present \\
\end{flushright}   
\begin{itemize}
\item Academic Teaching and Research Assistant for various Computer Science and Software Engineering courses. Taught introductory programming in Java, software design with UML, networking, operating systems and computer architecture courses.
\end{itemize}


\textbf{Java Software Developer} \\ 
Nakina Systems, Ottawa, ON
\begin{flushright}   
September 2008 - December 2010 \\
\end{flushright}   
\begin{itemize}
\item Developed  Java Enterprise and database driven applications. Worked on J2EE, client APIs, scripting interfaces, GWT and UI design, Database design and refactoring, Eclipse plugin and RCP development.
\item Evaluated and recommended test automation tools and determined suitability with various development tools
\item Developed and Implemented Test suites and wrote test cases for - unit level, functional and integration testing
\item Refactored and added components to the internal API’s of a Network Operating System in C and Java.
\item Designed and Developed a rich client application intended to build adapters (adapter is a software component which communicates with networks elements) using the Eclipse RCP and other powerful Java technologies.
\item Designed and Developed test clients used as test scenarios
\item Able to use different technologies such as SWT, JET, EMF, Xtext, Xpand, JFace, GMF and the concept of Eclipse plug-ins to create RCP applications.
\item Realized major and minor changes on the architecture of a J2EE Web Application.
\end{itemize}


\textbf{Capstone Project} \\ 
University of Ottawa, ON
\begin{flushright}  
January 2009 - December 2009 \\
\end{flushright}  
\begin{itemize}
\item Created the entire architecture of Web application using the framework ASP.MVC. Worked on ASP.MVC, Spring framework (Dependency injection), Hibernate, Rhino Mocks, jQuery, JSON, HTML5, JavaScript and AJAX.
\item Designed the Database model (Hibernate, SQLServer) and the Business model of the Web Application.
\item Interacted with the client to assess needs and solicit feedback
\item Worked cooperatively with colleagues at university to complete the project according to deadlines 
\end{itemize}

\textbf{Programmer} \\ 
Conseil des écoles catholiques de langue française du Centre-Est, Ottawa
\begin{flushright}  
January 2008 - May 2008 \\
\end{flushright}  

\begin{itemize}
\item Analyzed, designed and programmed a Web application for helping the orientation counselors of the CECLF to manage and to visualize student’s data.
\item Able to use different technologies such as Ajax, JavaScript, XML, Flash and ASP.NET for creating Web applications.
\item Wrote advanced SQL queries, triggers and Oracle stored procedures.
\end{itemize}

\textbf{Programmer} \\ 
Conseil des écoles catholiques de langue française du Centre-Est, Ottawa
\begin{flushright}  
May 2007 - August 2007 \\
\end{flushright}  
\begin{itemize}
\item Built and developed excellent skills in interpersonal relations and problem resolution while bringing solutions to some technical problems
\item Learned important aspects from ASP.NET such as the creation of user controls, the access to relational data (ADO.NET), the Session variables, optimization, configuration, deployment and the security of an application ASP.NET.
\item Created dynamic and sophisticated reports using Crystal Reports XI, tool provided with Visual Studio.NET.
\item Able to incorporate the AJAX technologies in designs Web.
\item Showed excellent team work while collaborating with other team members
\end{itemize}

\section{Education}

\begin{entrylist}
  \entry
    {2011-2015}
    {Ph.D., {\normalfont Computer Science}}
    {University of Ottawa, Ontario}
    {\emph{Reverse Engineering of Object-oriented software systems. }}
  \entry
    {2010-2011}
    {M.Sc., {\normalfont Computer Science}}
    {University of Ottawa, Ontario}
    {Specialization in Software Engineering}
  \entry
    {2005-2009}
    {B.Sc., {\normalfont Software Engineering (Coop)}}
    {University of Ottawa, Ontario}
    {Nortel's bursary}
  \entry
    {2003-2005}
    {Computer Science}
    {Outaouais College, Québec}
    {Followed a three-year technical program in Cégep.}
\end{entrylist}


\section{Technical Skills and Knowledge}

\begin{description}
\item [Software Design] Excellent understanding of the software engineering process. UML, N-Tier Architecture, Design Patterns, UML Metamodel, RUP, Scrum and XP Agile Processes. 
\item [Multi Programming and Network Programming] Java Threads and Client-Server applications
\item [Programming Languages] C/C++, Java, C\#, Visual Basic, MATLAB, Prolog and Ruby.
\item [Real Time Systems] Real-Time UML, SDL, Telelogic TAU
\item [Web Development] HTML, ASP.NET, ASP.MVC, JSP, EJB, JQuery, CSS, JavaScript, XML, PHP, AJAX, Java Applets, Java RMI, HTTPUnit, WCAG and W3C (Standards), Weblogic, Google API.
\item [Quality Assurance] Code coverage techniques, Mock Testing with MockRunner, Database Testing with dbUnit, Web Testing with Jetty and Cactus and Web Performance Testing with JMeter, jUnit.
\item [Data Mining] Knowledge of data mining algorithms and statistics
\item [Eclipse IDE Technologies] EMF, xText, Xpand, MDT, OCL Ecore, GMF, GEF, Eugenia
\item [Mobile Development] Windows Phone and Android SDK.
\item [Database Development] MS SQLServer, PostgreSQL,  MySQL, Oracle Databases, Hibernate, iBATIS, DBUnit
\item [Operating Systems] UNIX/LINUX, Windows Systems
\item [Graphical User Interface] Java Swing, AWT, Visual Basic, SWT, JSF
\item [IDE and Software] NetBeans, Eclipse 3.4.x, Visual Studio, GlassFish, StarTeam, Twiki, BugZilla, RSM, Visio, Aptana, Dreamweaver, DOORS, JUCMNav, jMeter, Assembla, SVN, CVS, Git.
\end{description}

\section{References}

\textbf{Available upon request}

%%% This piece of code has been commented by Karol Kozioł due to biblatex errors. 
% 
%\printbibsection{article}{article in peer-reviewed journal}
%\begin{refsection}
%  \nocite{*}
%  \printbibliography[sorting=chronological, type=inproceedings, title={international peer-reviewed conferences/proceedings}, notkeyword={france}, heading=subbibliography]
%\end{refsection}
%\begin{refsection}
%  \nocite{*}
%  \printbibliography[sorting=chronological, type=inproceedings, title={local peer-reviewed conferences/proceedings}, keyword={france}, heading=subbibliography]
%\end{refsection}
%\printbibsection{misc}{other publications}
%\printbibsection{report}{research reports}

\newpage


\end{document}
